Versatile Robust Clustering of Ad Hoc Cognitive Radio Network

### 2016-03-26 journal-draft/bare_jrnl_comsoc.tex
polished section 6, not done

\subsection{Phase II - Membership Clarification}
%\subsubsection*{Problem Description}
After applying phase I of ROSS to the example in Figure~\ref{fig1}, the resulted clusters are shown in Figure~\ref{fig2}.
We notice nodes $A, B, D$ are included in more than one cluster. 
We refer these nodes as \textit{debatable nodes} as their cluster affiliations are not clear, and the clusters which include the debatable node $i$ are called \textit{claiming clusters} of node $i$, and are denoted as $S_i$.  
Actually, debatable nodes extensively exist in CRN with larger scale.
Figure~\ref{percentage_overlapping_node} shows the percentage of debatable nodes increases when the CRN network becomes denser.
Debatable nodes should be exclusively associated with only one cluster and be removed from the other claiming clusters, this procedure is called \textit{cluster membership clarification}.
We will introduce the solution for cluster membership clarification in the following.

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.7\linewidth]{percentage_overlapping_node.pdf}
  \caption{The percentage of debatable nodes after phase I of ROSS.}\label{percentage_overlapping_node}
\end{figure}

@@

In order to highlight the amount of control signalling only for clustering, we omit the process of neighbourhood discovery, which is premise for all clustering schemes.
According to~\cite{complexity_aggregation_2011}, the message complexity is defined as the number of messages used by all nodes.
To have the same criterion to compare the overhead of signalling, we count \textit{the number of transmissions of control messages}, without distinguishing they are sent with broadcast or unicast.
This metric is Synonymous with \textit{the number of updates} discussed in Section~\ref{ross}.

@@

As to the centralized scheme, except for the calculation in the centralized control device, it also involves two phases of control message transmission.
The first phase is information aggregation, in which every CR node's channel availability and neighbourhood is sent to the centralized controller.
The second phase is broadcasting, where the final clustering solution is disseminated over the network to every CR node.
%As basic communication primitive for wireless networks, 
We adopt the algorithm proposed in~\cite{Efficient_broadcasting_gathering_adhoc} to broadcast and gather information as the algorithm is simple and self-stabilizing.
This scheme needs building a backbone structure to support the communication, we use our generated cluster heads as the backbone and the debatable nodes as the gateway nodes between the backbone nodes.
As the backbone is built once and can support transmission for multiple times, the messages involved in the clustering process are not included.
Every CR node can be informed if the cluster heads broadcast the message sent from the controller or other cluster heads, then the number of transmission is $h+m$.
As to information gathering, we assume that every cluster member sends the spectrum availability and its ID to its cluster head, which further forwards or the message to the controller.
The number of transmission for information gathering is $N$.
%As we adopt a simplified communication model, node's transmission is not influenced by collision or interference, 
%Our simulation doesn't consider the behaviour in the physical layer, 
The number of transmission is depicted in Figure~\ref{control_msg}.
Note that the curve for the centralized scheme is from theoretical analysis, which is $h+m+N$ as discussed beforehand.
Note the overhead involved to construct the backbone (clusters) is not included.
%Assume we use OSPF~\cite{BCJ10} to aggregate and disseminate information, then the best and worst complexity for is $\mathcal{O}(E)$, where $E$ is the number of edges in the graph which corresponds to the network.
%The minimum number of edges is $n-1$ when the nodes form a line and each node has at more two neighbours, and the maximum number is $N*(N-1)/2$ when the nodes form a complete graph.
%Thus the best message complexity of the centralized scheme is $\mathcal{O}{(N)}$ and the worst is $\mathcal{O}{(N^2)}$.

@@

>>>>

\subsection{Phase II - Membership Clarification}
%\subsubsection*{Problem Description}
After applying phase I of ROSS to the example in Figure~\ref{fig1}, the resulted clusters are shown in Figure~\ref{fig2}.
We notice nodes $A, B, D$ are included in more than one cluster. 
We refer these nodes as \textit{debatable nodes} as their cluster affiliations are not clear, and the clusters which include the debatable node $i$ are called \textit{claiming clusters} of node $i$, and are denoted as $S_i$.  
Actually, debatable nodes extensively exist in CRN with larger scale.
Debatable nodes should be exclusively associated with only one cluster and be removed from the other claiming clusters, this procedure is called \textit{cluster membership clarification}.
We will introduce the solution for cluster membership clarification in the following.

@@

In order to highlight the amount of control signalling only for clustering, we omit the process of neighbourhood discovery, which is premise for all clustering schemes.
According to~\cite{complexity_aggregation_2011}, the message complexity is defined as the number of messages used by all nodes.
To have the same criterion to compare the overhead of signalling, we count \textit{the number of transmissions of control messages}, without distinguishing they are sent with broadcast or unicast.
This metric is synonymous with \textit{the number of updates} discussed in Section~\ref{ross}.

@@

As to the centralized scheme, except for the calculation in the centralized control device, it also involves two phases of control message transmission.
The first phase is information aggregation, in which every CR node's channel availability and neighbourhood is sent to the centralized controller.
The second phase is broadcasting, where the final clustering solution is disseminated over the network to every CR node.
%As basic communication primitive for wireless networks, 
We adopt the algorithm proposed in~\cite{Efficient_broadcasting_gathering_adhoc} to broadcast and gather information as the algorithm is simple and self-stabilizing.
This scheme needs building a backbone structure to support the communication, we use our generated cluster heads as the backbone and the debatable nodes as the gateway nodes between the backbone nodes.
As the backbone is built once and can support transmission for multiple times, the messages involved in the clustering process are not included.
Every CR node can be informed if the cluster heads broadcast the message sent from the controller or other cluster heads, then the number of transmission is $h+m$.
As to information gathering, we assume that every cluster member sends the spectrum availability and its ID to its cluster head, which further forwards or the message to the controller.
The number of transmission for information gathering is $N$.
%As we adopt a simplified communication model, node's transmission is not influenced by collision or interference, 
%Our simulation doesn't consider the behaviour in the physical layer,

%Assume we use OSPF~\cite{BCJ10} to aggregate and disseminate information, then the best and worst complexity for is $\mathcal{O}(E)$, where $E$ is the number of edges in the graph which corresponds to the network.
%The minimum number of edges is $n-1$ when the nodes form a line and each node has at more two neighbours, and the maximum number is $N*(N-1)/2$ when the nodes form a complete graph.
%Thus the best message complexity of the centralized scheme is $\mathcal{O}{(N)}$ and the worst is $\mathcal{O}{(N^2)}$.

@@

Figure~\ref{percentage_overlapping_node} shows the percentage of debatable nodes increases when the CRN network becomes denser, from which we can obtain the value of $m$.
\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.7\linewidth]{percentage_overlapping_node.pdf}
  \caption{The percentage of debatable nodes after phase I of ROSS.}\label{percentage_overlapping_node}
\end{figure}

Figure~\ref{control_msg} shows the number of transmissions of SOC, the upper bound of the number of transmissions for ROSS, and the analytical number of transmissions of the centralised scheme. 
Note that the curve for the centralized scheme is from theoretical analysis, which is $h+m+N$ as discussed beforehand.
Note the overhead involved to construct the backbone (clusters) is not included.
